---
title: "Climwin_MassA.Rmd"
author: "Ivan Bizberg"
date: "10/25/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---


```{r, global-options, include=FALSE}
knitr::opts_chunk$set(fig.height = 10, fig.width = 15, error = FALSE)
```

Libraries
```{r message=FALSE, warning=FALSE}
# Data wrangling
library(tidyverse)
library(lubridate)
library(magrittr)
# Analisis
library(climwin)
library(lme4)
# Model selection
library(MuMIn)
library(bbmle)
library(performance)
# Plotting
library(ggthemes)
library(effects)
library(Greg)
library(rms)
library(kableExtra)
```

```{r}
path = "conducta"
setwd(str_glue("C:/Users/{path}/Dropbox/PHD/Git/Climwin_MassA"))
getwd()
```


```{r}
# Climatic data
ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>% 
  mutate(Chl = if_else(abs(Chl) > mean(Chl, na.rm = T)+3*sd(Chl, na.rm = T), NA_real_, Chl)) %>% 
  mutate(Area_Rain = if_else(abs(Area_Rain) > mean(Area_Rain, na.rm = T)+3*sd(Area_Rain, na.rm = T), NA_real_, Area_Rain)) %>% 
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% mutate(SST = as.numeric(SST))
```


```{r}
# Biological data
MotherBio <- read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/RawData4.5.csv"),sep =",",
                 header = T, stringsAsFactors = F) %>% rename(Clutch = PUESTA, Brood = NIDADA)
```

```{r}
# Fix data
BioData <- MotherBio %>% #select(sort(colnames(.))) %>% 
  filter(SEMANIPULO == "f") %>%
  # Remove data errors and birds that were measure before their time
  filter(!((LastAge1 %in% c(-50 : 65)))) %>% # Remove birds that where measure before 70 days
  mutate_at(vars(ESTECLOS1, ESTECLOS2, ESTECLOS3), ymd) %>% 
  mutate(DATE1 = ESTECLOS1 + 70) %>% 
  mutate(DATE2 = ESTECLOS2 + 70) %>% 
  mutate(DATE3 = ESTECLOS3 + 70) %>% 
  filter(!Nest_OrderFemale %in% c(2,3)) %>% # Remove females re-nests
  select(WORKYEAR, NIDO, PROPORTIONALRANK, LayRank, HatchRank, CoupleExpLocal, Clutch, Brood, 
         EstHatchAsynchro12_, EstHatchAsynchro13_, EstHatchAsynchro23_,
         CondCohabtime1, CondCohabtime2, CondCohabtime3,
         CONFIRMHEMB, CONFIRMMACH,
         contains(c("ANILLO","AGE")), ends_with(c("1", "2", "3")), 
         -contains(c("90", "HERIDO", "DISTANCIA", "SENCONTRO"))) %>% 
  mutate_all(as.character) %>% 
  pivot_longer(cols = all_of(ends_with(c("1","2","3"))), 
               names_to = c("columns", "ChickRank"), 
               names_pattern = "(.*)(.)") %>% 
  pivot_wider(names_from = "columns")

FixBioData <- BioData %>% mutate_at(vars(DATE), ymd) %>% 
  mutate_at(vars(BodyCondSMI, PESO70, WORKYEAR, LastAge),as.numeric) %>% 
  filter(ChickRank == "1") %>% 
  filter(!(abs(PESO70)>mean(PESO70, na.rm = T)+3*sd(PESO70, na.rm = T))) %>%
  mutate(ULNA70 = as.numeric(ULNA70)) %>% 
  filter(!(abs(ULNA70)>mean(ULNA70, na.rm = T)+3*sd(ULNA70, na.rm = T))) 

boxplot(FixBioData$PESO70) # check outliers 
write_csv(FixBioData, "ClimWinBodyCond_1.csv")
```

### Import created data
```{r, results=FALSE}
FixedBioData <- read_csv("ClimWinBodyCond_1.csv")
ClimBioData <- FixedBioData %>%
  select(WORKYEAR, NIDO, ChickRank, LastAge, DATE, PESO70, BodyCondSMI, Brood, ULNA70) %>% 
  na.omit()

```


# Climwin chicks 1

# Finding window for chlorophyll-a

```{r message=FALSE, warning=FALSE}
Bio <- ClimBioData %>% filter(DATE >= "2003-05-01") %>%
  mutate_at(vars(WORKYEAR), as.factor) %>% 
  na.omit()
```

```{r}
Clim = ClimData %>% select(Date , Chl) %>%
  # filter(!Chl > 70) %>% # remove one oultlier
  na.omit()
```

##Climwin analysis

```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Chl), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(15, 0),
                      type = "relative",
                      stat = c("sum", "max", "min"),
                      func = c("quad", "lin"),
                      cmissing = "method1")

```
### Results

```{r}
Comb <- (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)) ; as.data.frame(Comb)
```
```{r}
n <- Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r fig.height = 5, fig.width = 8, fig.align="center"}
plotdelta(dataset = Results)
```

#### Extract data Chl
```{r}
ClimVar <- "Chl"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
ExtractedData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(ExtractedData, str_glue("WinBodyCond{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimRand <- randwin(repeats = 16,
                    xvar = list(ClimVar = Clim$Chl),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(15, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "AIC", sample.size = 16)

plothist(Results, ClimWinRand)

```



# Data Bio 1989
```{r}
# Biological data
Bio = ClimBioData %>% filter(WORKYEAR > "1989") %>%
  mutate_at(vars(WORKYEAR), as.factor) %>% 
  na.omit()
```

# Finding window for SST
```{r}
# Climatic data
Clim <- ClimData %>% select(Date , SST) %>%
  na.omit()
```

##Climwin analysis

```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$SST), # Climatic variable
                      bdate = Bio$DATE,
                      cdate = Clim$Date,
                      baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(17, 0),
                      type = "relative",
                      stat = c("mean", "max", "min"),
                      func = c("quad", "lin"),
                      cmissing = "method1")
```
### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); as.data.frame(Comb)
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```

#### Extract data SST
```{r}
ClimVar = "SST"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
ExtractedData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(ExtractedData, str_glue("WinBodyCond{ClimVar}.csv"))
```

## Randomization
```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimRand <- randwin(repeats = 16,
                    xvar = list(ClimVar = Clim$SST),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(17, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "AIC", sample.size = 29)

plothist(Results, ClimWinRand)

```



# Finding window for Wind

```{r}
# Climatic data
Clim = ClimData %>%
  select(Date , Wind) %>%
  na.omit()
```

##Climwin analysis Wind
```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Wind), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(17, 0),
                      type = "relative",
                      stat = c("min", "max", "mean"),
                      func = c("lin", "quad"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% add_rownames() %>% arrange((DeltaAICc)); as.data.frame(Comb)
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```

#### Extract data Wind
```{r}
ClimVar = "Wind"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
ExtractedData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(ExtractedData, str_glue("WinBodyCond{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Wind),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(17, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "AIC", sample.size = 29)

plothist(Results, ClimWinRand)

```

# Finding window for Rain 

```{r}
# Climatic data
Clim = ClimData %>%
  select(Date , Rain, NdaysRain) %>%
  na.omit()
```

## Climwin analysis Rain

```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Rain), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(20, 0),
                      type = "relative",
                      stat = c("sum", "max"), # error with min
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% add_rownames() %>% arrange((DeltaAICc)); as.data.frame(Comb)
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```

#### Extract data Rain
```{r}
ClimVar = "Rain"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
ExtractedData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(ExtractedData, str_glue("WinBodyCond{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimRand <- randwin(repeats = 16,
                    xvar = list(ClimVar = Clim$Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(20, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```


### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "AIC", sample.size = 29)

plothist(Results, ClimWinRand)

```


# Finding window for Area_Rain

```{r}
# Climatic data
Clim = ClimData %>%
  select(Date, Area_Rain, NdaysArea_Rain, NdaysArea_RainMedium) %>%
  na.omit()
```

##Climwin analysis 

```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Area_Rain), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio,
                                      control=lmerControl(optimizer="bobyqa",
                                                          optCtrl=list(maxfun=2e6))),
                      cinterval = "week",
                      range = c(21, 0),
                      type = "relative",
                      stat = c("max", "sum"), # error with min convergence with sum/quad (but fixed with bobyqa)
                      func = c("lin", "quad"), # Can't use log and inv because of zeros
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% add_rownames() %>% arrange((DeltaAICc)); as.data.frame(Comb)
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```
#### Extract data Area_Rain
```{r}
ClimVar = "Area_Rain"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
ExtractedData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(ExtractedData, str_glue("WinBodyCond{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results=FALSE, cache=TRUE, warning=FALSE}
ClimRand <- randwin(repeats = 16,
                    xvar = list(ClimVar = Clim$Area_Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70 ~ ULNA70 + (1|WORKYEAR), REML = F, data = Bio, 
                                    control=lmerControl(optimizer="bobyqa",
                                                          optCtrl=list(maxfun=2e6))),
                    cinterval = "week",
                    range = c(21, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "AIC", sample.size = 29)

plothist(Results, ClimWinRand)

```

# Compile new data
```{r, results=FALSE, warning=FALSE}
Chl <- read_csv("WinBodyCondChl.csv") %>% select(1:2, NIDO, WORKYEAR) 
SST <- read_csv("WinBodyCondSST.csv") %>% select(1:2, NIDO, WORKYEAR) 
Area_Rain <- read_csv("WinBodyCondArea_Rain.csv") %>% select(1:2, NIDO, WORKYEAR) 

Mother <- read_csv("ClimWinBodyCond_1.csv")

FinalData <- plyr::join_all(list(Mother, Chl, SST, Area_Rain), by = c("NIDO", "WORKYEAR"), type = "left") 
write_csv(FinalData, "DATAWinBodyCond_1.csv")
```









# Which variable need to be refitted?
```{r}
Final_Data = read.csv("DATAWinBodyCond_1.csv")

LmmData = Final_Data %>%  
  # filter(CONFIRMHEMB == "TRUE") %>%
  mutate_at(vars(PROPORTIONALRANK, BodyCondSMI, Brood, Chl, SST, Area_Rain, CondCohabtime, 
                 AGEHEMB, AGEMACH),
            arm::rescale) %>% 
  select(WORKYEAR, 
         # ANILLOMACH, AGEMACH,
         # ANILLOHEMB, AGEHEMB,
         # CoupleExpLocal,
         # CondCohabtime,
         BodyCondSMI,
         # PROPORTIONALRANK, 
         Brood, Chl, SST, Area_Rain) %>% na.omit()
```

```{r}
Bestcond <- lmer(
  BodyCondSMI ~ #Brood +
    # CoupleExpLocal +
    # CondCohabtime +
    # PROPORTIONALRANK + 
    Chl + 
    I(Chl^2) + 
    SST + 
    I(SST^2) + 
    Area_Rain +
    I(Area_Rain^2) +
    # AGEHEMB +
    # I(AGEHEMB^2) +
    (1 | WORKYEAR), #+ (1|ANILLOHEMB),
  REML = FALSE,
  data = LmmData) 

sjPlot::tab_model(Bestcond)
```
We need to refit signals relevant for body Condition in this case we have Chl, SST, Wind, NArea_Rain 
```{r}
# Check vif
check_collinearity(Bestcond)
```


















# Refiting Variables (Chl_2, SST_2, Area_Rain_2, Wind)
### Data For refitting
```{r, message=FALSE}
BioData = read_csv(str_glue("DATAWinBodyCond_1.csv")) %>% 
  select(WORKYEAR, NIDO, ChickRank, LastAge, DATE, PESO70, BodyCondSMI, Brood, ULNA70, 59 : 64) %>% glimpse()
```

```{r}
# Climatic data
ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>% 
  mutate(Chl = if_else(abs(Chl) > mean(Chl, na.rm = T)+3*sd(Chl, na.rm = T), NA_real_, Chl)) %>% 
  mutate(Area_Rain = if_else(abs(Area_Rain) > mean(Area_Rain, na.rm = T)+3*sd(Area_Rain, na.rm = T), NA_real_, Area_Rain)) %>% 
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% mutate(SST = as.numeric(SST))
```

# Reffiting Chlorophyll-a
```{r}
Bio = BioData %>% filter(DATE >= "2003-05-01") %>%
  mutate(across(c(WORKYEAR), as.factor)) %>% 
  # mutate(across(c(where(is.numeric), -ChickRank), arm::rescale)) %>% # If we want to rescale but don't make any diference
  na.omit() %>% glimpse()
```
 
```{r}
# Impute manually missing data 
Missing <- c("35/2007", "18/2011", "36/2013", "37/2014", "45/2014", "42/2018")

Missing_data <- as.Date(paste0('1/', Missing), '%u/%U/%Y')

Clim = ClimData %>% select(Date , Chl) %>% drop_na() %>% 
  rbind(., data.frame(Date = Missing_data, Chl = NA)) %>% # add missing values 
  arrange(Date) %>% 
  mutate(Chl = if_else(is.na(Chl), (lag(Chl,1) + lead(Chl,1) + lag(Chl, 2) + lead(Chl, 2))/4, Chl)) %>% 
  distinct(Date, .keep_all = T)

```

##Climwin analysis

```{r, message=FALSE, results=FALSE, warning=FALSE, cache=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Chl), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70 ~ ULNA70 + SST_2 + Area_Rain_2 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(15, 0),
                      type = "relative",
                      stat = c("min", "max", "sum"),
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)) ; as.data.frame(Comb)
```


```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```
#### Average results
```{r}
medwin(ClimWin[[n]]$Dataset) # calculate mean open window and mean close window from the best model base on the 95% confidence 

dataset <- ClimWin[[n]]$Dataset

ConfidenceSet <- dataset[which(cumsum(dataset$ModWeight) <= 0.95), ]

sum(ConfidenceSet$ModelBeta*ConfidenceSet$ModWeight)
```

#### Extract data RefittedChl
```{r}
ClimVar = "RefittedChl"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinBodyCond{ClimVar}.csv"))
```
## Randomization
```{r, message=FALSE, results=FALSE, warning=FALSE, cache=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Chl),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70 ~ ULNA70 + SST_2 + Area_Rain_2 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(15, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 16)

plothist(Results, ClimWinRand)

```
## Weight Chl
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
# Bio_Scale <- Bio %>% mutate(across(c(HatchAsync, PROPORTIONALRANK, SST_2), scale))
# Clim_Scale <- Clim %>% mutate(across(c(Chl), scale))
dev.new(noRStudioGD = T)
weight <- weightwin(n = 15,
                    xvar = list(ClimVar = Clim$Chl),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70~ ULNA70 + SST_2 + Area_Rain_2 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(15, 0),
                    type = "relative",
                    func = tidy_func,
                    weightfunc = "W",
                    cmissing = "method1",
                    par = c(3, 0.2, 0))
```
#### Weight Chl results
```{r}
Weight_results <- weight$iterations %>% rownames_to_column() %>% arrange(deltaAICc); Weight_results # Show iteration results 
n <- Weight_results[1, 1] %>% as.numeric()
Best_iter <- weight[[n]]$WeightedOutput; Best_iter # Best model interation
```


```{r, warning=FALSE}
plot(weight[[10]]$Weights, type = "line")
```
We need to compare the AIC from the slidingwin function and from the weightwin to see with function explain better the variation in brood reduction either a weight with uniform distribution or a weight with Weibull distribution. 
Here we can se that the better model is with _..._ function

### Randomization weight
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
dev.new(noRStudioGD = T)
WeightRand <- randwin(repeats = 15,
                      window = "weighted",
                      xvar = list(ClimVar = Clim$Chl),
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70~ ULNA70 + SST_2 + Area_Rain_2 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(15, 0),
                      type = "relative",
                      func = tidy_func,
                      cmissing = "method1",
                      weightfunc = "W", par = c(3, 0.2, 0))

```
#### Results weight
```{r}
pvalue(dataset = weight[[n]]$WeightedOutput, datasetrand = WeightRand[[1]], metric = "AIC")
```


# Reffiting SST

```{r}
Missing <- c("33/1988", "37/1991", "37/1992", "41/1994", "15/1997", "18/2001", 
             "50/2001", "16/2002", "35/2004", "5/2012", "50/2012", "8/2013", 
             "36/2013", "51/2017")
Clim = ClimData %>% select(Date , SST) %>%
  #Imput manually data for 6 missing weeks 
  mutate(Weeks = week(Date)) %>% 
  mutate(Days = day(Date)) %>% 
  mutate(Year = year(Date)) %>% 
  mutate(Weeks_Year = paste0(.$Weeks, "/", .$Year)) %>% 
  filter(!(is.na(SST) & !Weeks_Year %in% Missing)) %>% 
  group_by(Weeks_Year) %>% mutate(n = 1, n = cumsum(n)) %>% ungroup() %>% 
  filter(!(n > 1 & is.na(SST))) %>% select(-n) %>% # Remove duplicate when SST is NA
  # manual cmissing = method1 (input with the mean of 2 last and 2 forward observations)
  arrange(Date) %>% 
  mutate(SST = if_else(
    is.na(SST),
    (lag(SST,1) + lead(SST,1) + lag(SST, 2) + lead(SST, 2))/4,
    SST
  )) %>% 
  filter(!SST < 5) %>% # Outliers where check
  select(Date , SST)
```

##Climwin analysis

```{r, message=FALSE, results=FALSE, warning=FALSE, cache=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$SST), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70 ~ ULNA70 + Chl_2 + Area_Rain_2 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(15, 0),
                      type = "relative",
                      stat = c("min", "max", "mean"),
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); as.data.frame(Comb)
```


```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```
#### Average results
```{r}
medwin(ClimWin[[n]]$Dataset) # calculate mean open window and mean close window from the best model base on the 95% confidence 

dataset <- ClimWin[[n]]$Dataset

ConfidenceSet <- dataset[which(cumsum(dataset$ModWeight) <= 0.95), ]

sum(ConfidenceSet$ModelBeta*ConfidenceSet$ModWeight)
```
#### Extract data RefittedSST
```{r}
ClimVar = "RefittedSST"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinBodyCond{ClimVar}.csv"))
```
## Randomization
```{r, message=FALSE, results=FALSE, warning=FALSE, cache=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$SST),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70 ~ ULNA70 + Chl_2 + Area_Rain_2 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(15, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 16)

plothist(Results, ClimWinRand)

```

## Weight SST
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
# Bio_Scale <- Bio %>% mutate(across(c(HatchAsync, PROPORTIONALRANK, SST_2), scale))
# Clim_Scale <- Clim %>% mutate(across(c(Chl), scale))
dev.new(noRStudioGD = T)
weight <- weightwin(n = 15,
                    xvar = list(ClimVar = Clim$SST),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70~ ULNA70 + Chl_2 + Area_Rain_2 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(15, 0),
                    type = "relative",
                    func = tidy_func,
                    weightfunc = "W",
                    cmissing = "method1",
                    par = c(3, 0.2, 0))
```
#### Weight SST results
```{r}
Weight_results <- weight$iterations %>% rownames_to_column() %>% arrange(deltaAICc); Weight_results # Show iteration results 
n <- Weight_results[1, 1] %>% as.numeric()
Best_iter <- weight[[n]]$WeightedOutput; Best_iter # Best model interation
```


```{r, warning=FALSE}
plot(weight[[10]]$Weights, type = "line")
```
We need to compare the AIC from the slidingwin function and from the weightwin to see with function explain better the variation in brood reduction either a weight with uniform distribution or a weight with Weibull distribution. 
Here we can se that the better model is with _..._ function

### Randomization weight
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
dev.new(noRStudioGD = T)
WeightRand <- randwin(repeats = 15,
                      window = "weighted",
                      xvar = list(ClimVar = Clim$SST),
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70~ ULNA70 + Chl_2 + Area_Rain_2 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(15, 0),
                      type = "relative",
                      func = tidy_func,
                      cmissing = "method1",
                      weightfunc = "W", par = c(3, 0.2, 0))

```
#### Results weight
```{r}
pvalue(dataset = weight[[n]]$WeightedOutput, datasetrand = WeightRand[[1]], metric = "AIC")
```




# Reffiting Area rain

```{r}
Clim = ClimData %>% select(Date , Area_Rain) %>%
  na.omit()
```

## Climwin analysis

```{r, message=FALSE, results=FALSE, warning=FALSE, cache=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Area_Rain), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70 ~ ULNA70 + Chl_2 + SST_2 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(16, 0),
                      type = "relative",
                      stat = c("mean", "min", "max", "sum"),
                      func = c("quad", "lin"), # Model can't run with log or inv 
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); as.data.frame(Comb)
```


```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```
#### Average results
```{r}
medwin(ClimWin[[n]]$Dataset) # calculate mean open window and mean close window from the best model base on the 95% confidence 

dataset <- ClimWin[[n]]$Dataset

ConfidenceSet <- dataset[which(cumsum(dataset$ModWeight) <= 0.95), ]

sum(ConfidenceSet$ModelBeta*ConfidenceSet$ModWeight)
```
#### Extract data ReffitedAreaRain
```{r}
ClimVar = "RefittedAreaRain"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinBodyCond{ClimVar}.csv"))
```
## Randomization
```{r, message=FALSE, results=FALSE, warning=FALSE, cache=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Area_Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70 ~ ULNA70 + Chl_2 + SST_2 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(10, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 16)

plothist(Results, ClimWinRand)

```




## Weight Area_Rain
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
# Bio_Scale <- Bio %>% mutate(across(c(HatchAsync, PROPORTIONALRANK, SST_2), scale))
# Clim_Scale <- Clim %>% mutate(across(c(Chl), scale))
dev.new(noRStudioGD = T)
weight <- weightwin(n = 15,
                    xvar = list(ClimVar = Clim$Area_Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = lmer(PESO70~ ULNA70 + Chl_2 + SST_2 + (1|WORKYEAR), REML = F, data = Bio),
                    cinterval = "week",
                    range = c(16, 0),
                    type = "relative",
                    func = tidy_func,
                    weightfunc = "W",
                    cmissing = "method1",
                    par = c(3, 0.2, 0))
```
#### Weight Area_Rain results
```{r}
Weight_results <- weight$iterations %>% rownames_to_column() %>% arrange(deltaAICc); Weight_results # Show iteration results 
n <- Weight_results[1, 1] %>% as.numeric()
Best_iter <- weight[[n]]$WeightedOutput; Best_iter # Best model interation
```


```{r, warning=FALSE}
plot(weight[[10]]$Weights, type = "line")
```
We need to compare the AIC from the slidingwin function and from the weightwin to see with function explain better the variation in brood reduction either a weight with uniform distribution or a weight with Weibull distribution. 
Here we can se that the better model is with _..._ function

### Randomization weight
```{r, eval=TRUE, cache=TRUE, results="hide", message=FALSE}
dev.new(noRStudioGD = T)
WeightRand <- randwin(repeats = 15,
                      window = "weighted",
                      xvar = list(ClimVar = Clim$Area_Rain),
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = lmer(PESO70~ ULNA70 + Chl_2 + SST_2 + (1|WORKYEAR), REML = F, data = Bio),
                      cinterval = "week",
                      range = c(16, 0),
                      type = "relative",
                      func = tidy_func,
                      cmissing = "method1",
                      weightfunc = "W", par = c(3, 0.2, 0))

```
#### Results weight
```{r}
pvalue(dataset = weight[[n]]$WeightedOutput, datasetrand = WeightRand[[1]], metric = "AIC")
```




# Final compilation of data
```{r, results=FALSE, message=FALSE}
# Compile new data
RefittedChl = read_csv("WinBodyCondRefittedChl.csv") %>% 
  select(1:2, NIDO, WORKYEAR)
RefittedSST = read_csv("WinBodyCondRefittedSST.csv") %>% 
  select(1:2, NIDO, WORKYEAR)
RefittedAreaRain = read_csv("WinBodyCondRefittedAreaRain.csv") %>% 
  select(1:2, NIDO, WORKYEAR)


NewMother = read_csv("ClimWinBodyCond_1.csv")

FinalData = plyr::join_all(list(NewMother, RefittedChl, RefittedSST, RefittedAreaRain), 
                           by = c("NIDO", "WORKYEAR"), 
                           type = "left") %>% glimpse()
write_csv(FinalData,("RefittedDATABodyCond_1.csv"))
```









# We need to add last reproductive effort from the mother

```{r}
FemaleCosts = read_csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/DATAFemaleCosts.csv")) %>%
  select(ANILLOHEMB, WORKYEAR, NIDO, LastParentalCare_ALL, LastParentalCare_Egg, LastParentalCare_Chick)
RefitData = read_csv("RefittedDATABodyCond_1.csv")

AddData = left_join(RefitData, FemaleCosts, by = c("ANILLOHEMB", "WORKYEAR", "NIDO"))
write_csv(AddData, "FinalRefittedDATABodyCond_1.csv")
```


# Final Result for brood reduction and climatic and enviromental factors

### Females
```{r}
FinalData = read_csv("RefittedDATABodyCond_1.csv") %>% 
  mutate(across(c(WORKYEAR, ANILLOHEMB, ANILLOMACH), as.factor)) %>%
  mutate_at(vars(RefittedSST, RefittedChl, RefittedAreaRain, ULNA70,
                 AGEHEMB, AGEMACH, CoupleExpLocal,
                 Cohabtime,
                 PROPORTIONALRANK, CondCohabtime), arm::rescale)
```


```{r}
# FinalData %>% names() %>% sort()  
LmmData = FinalData %>% 
  filter(CONFIRMHEMB == "TRUE") %>%
  filter(!ANILLOHEMB == "SA") %>%
  mutate(across(c(where(is.numeric), -PESO70, -Brood), ~scale(., center = T, scale = T))) %>%
  select(WORKYEAR, Brood, PESO70, ULNA70, 
         ANILLOHEMB, AGEHEMB,
         CoupleExpLocal,
         BodyCondSMI, 
         CondCohabtime,
         PROPORTIONALRANK, 
         RefittedSST, RefittedChl, RefittedAreaRain) %>% na.omit() %>% as.data.frame() %>% 
  glimpse()

Lmm_full = lmer(PESO70 ~ ULNA70 +
                  CondCohabtime + 
                  PROPORTIONALRANK +
                  RefittedChl +
                  I(RefittedChl^2) +
                  RefittedSST +
                  I(RefittedSST^2) +
                  RefittedAreaRain +
                  I(RefittedAreaRain^2) +
                  AGEHEMB +
                  I(AGEHEMB^2) +
                  CoupleExpLocal +
                  (1|WORKYEAR) + (1|ANILLOHEMB),
                na.action = "na.fail", REML = FALSE,
                data = LmmData)

sjPlot::tab_model(Lmm_full)

Lmm_NULL <- update(Lmm_full, . ~ . -(1|ANILLOHEMB))
AICtab(Lmm_full, Lmm_NULL) # keep female id as random effect
```
```{r}
# Plot
plot(allEffects(Lmm_full))
```
```{r}
# Final results
Summary <- summary(Lmm_full)
FixCoef <- Summary$coefficients %>% as.data.frame() %>% rownames_to_column("Terms")
RandCoef <- Summary$varcor %>% as.data.frame() %>% select(-var2) %>% rename(Terms = grp)
CI <- confint(Lmm_full) %>% as.data.frame() %>% rownames_to_column("Terms")
CoefTable <- CI %>% left_join(FixCoef, by = "Terms") %>% bind_rows(RandCoef)
write_csv(CoefTable, "FemaleResults.csv")
```

### Male 
```{r}
# FinalData %>% names() %>% sort()  
LmmData = FinalData %>% 
  filter(CONFIRMMACH == "TRUE") %>%
  filter(!ANILLOMACH == "SA") %>%
  select(WORKYEAR, Brood, PESO70, ULNA70,
         CondCohabtime,
         ANILLOMACH, AGEMACH,
         CoupleExpLocal,
         BodyCondSMI, 
         PROPORTIONALRANK, 
         RefittedSST, RefittedChl, RefittedAreaRain) %>% na.omit() %>% as.data.frame() %>% 
  glimpse()

Lmm_full = lmer(PESO70 ~ ULNA70 +
                  CondCohabtime + 
                  PROPORTIONALRANK +
                  RefittedChl +
                  I(RefittedChl^2) +
                  RefittedSST +
                  I(RefittedSST^2) +
                  RefittedAreaRain +
                  I(RefittedAreaRain^2) +
                  AGEMACH +
                  I(AGEMACH^2) +
                  CoupleExpLocal +
                  (1|WORKYEAR) + (1|ANILLOMACH),
                na.action = "na.fail", REML = FALSE,
                data = LmmData)


sjPlot::tab_model(Lmm_full)

Lmm_NULL <- update(Lmm_full, . ~ . -(1|ANILLOMACH))
AICtab(Lmm_full, Lmm_NULL) # keep male id as random effect

```
```{r}
# Plot
plot(allEffects(Lmm_full))
```
```{r}
# Final results
Summary <- summary(Lmm_full)
FixCoef <- Summary$coefficients %>% as.data.frame() %>% rownames_to_column("Terms")
RandCoef <- Summary$varcor %>% as.data.frame() %>% select(-var2) %>% rename(Terms = grp)
CI <- confint(Lmm_full) %>% as.data.frame() %>% rownames_to_column("Terms")
CoefTable <- CI %>% left_join(FixCoef, by = "Terms") %>% bind_rows(RandCoef)
write_csv(CoefTable, "MaleResults.csv")
```
### Final
```{r}
# FinalData %>% names() %>% sort()  
LmmData = FinalData %>% 
    filter(CONFIRMHEMB == "TRUE") %>%
  filter(!ANILLOHEMB == "SA") %>%
  select(WORKYEAR, Brood, PESO70, ULNA70,
         ANILLOHEMB,
         CondCohabtime,
         Brood,
         # CoupleExpLocal,
         BodyCondSMI, 
         PROPORTIONALRANK, 
         RefittedSST, RefittedChl, RefittedAreaRain) %>% na.omit() %>% as.data.frame() %>% 
  glimpse()

Sample_size <- LmmData %>% count()
write_csv(Sample_size, "Sample_size.csv")
Lmm_fullH = lmer(PESO70 ~ ULNA70 +
                  Brood + 
                  PROPORTIONALRANK +
                  RefittedChl +
                  I(RefittedChl^2) +
                  RefittedSST +
                  I(RefittedSST^2) +
                  RefittedAreaRain +
                  I(RefittedAreaRain^2) +
                  # CoupleExpLocal +
                  (1|WORKYEAR),
                na.action = "na.fail", REML = FALSE,
                data = LmmData)





FinalData = read_csv("FinalRefittedDATABodyCond_1.csv") %>% glimpse()
# FinalData %>% names() %>% sort()  
LmmData = FinalData %>% 
    filter(CONFIRMMACH == "TRUE") %>%
  filter(!ANILLOMACH == "SA") %>%
  # mutate(across(Brood, as.factor)) %>%
   mutate_at(vars(RefittedSST, RefittedChl, RefittedAreaRain, ULNA70,
                 AGEHEMB, AGEMACH, CoupleExpLocal,
                 Cohabtime,
                 PROPORTIONALRANK, CondCohabtime), arm::rescale) %>% 
  select(WORKYEAR, Brood, PESO70, ULNA70,
         ANILLOMACH,
         CondCohabtime,
         Brood,
         CoupleExpLocal,
         BodyCondSMI, 
         PROPORTIONALRANK, 
         RefittedSST, RefittedChl, RefittedAreaRain) %>% na.omit() %>% as.data.frame() %>% 
  glimpse()

Sample_size <- LmmData %>% count()
write_csv(Sample_size, "Sample_size.csv")
Lmm_fullM = lmer(PESO70 ~ ULNA70 +
                  CondCohabtime + 
                  PROPORTIONALRANK +
                  RefittedChl +
                  I(RefittedChl^2) +
                  RefittedSST +
                  I(RefittedSST^2) +
                  RefittedAreaRain +
                  I(RefittedAreaRain^2) +
                  CoupleExpLocal +
                  (1|WORKYEAR),
                na.action = "na.fail", REML = FALSE,
                data = LmmData)

sjPlot::tab_model(Lmm_fullH)


LmmNULLH <- update(Lmm_fullH, .~. + (1|ANILLOHEMB))
LmmNULLM <- update(Lmm_fullM, .~. + (1|ANILLOMACH))


AICtab(LmmNULLH, LmmNULLM, Lmm_fullH, Lmm_fullM, Lmm_full)
AICtab(LmmNULLH, Lmm_fullH)
```
### Best Final model
```{r}
# FinalData %>% names() %>% sort()  
LmmData = FinalData %>% 
  #  filter(CONFIRMHEMB == "TRUE") %>%
  # filter(!ANILLOHEMB == "SA") %>%
  select(WORKYEAR, Brood, PESO70, ULNA70,
         CondCohabtime,
         # ANILLOHEMB,
         Brood,
         # CoupleExpLocal,
         BodyCondSMI, 
         PROPORTIONALRANK, 
         RefittedSST, RefittedChl, RefittedAreaRain) %>% na.omit() %>% as.data.frame() %>% 
  glimpse()

Sample_size <- LmmData %>% count()
write_csv(Sample_size, "Sample_size.csv")
Lmm_full = lmer(PESO70 ~ ULNA70 +
                  PROPORTIONALRANK +
                  CondCohabtime + 
                  RefittedChl +
                  I(RefittedChl^2) +
                  RefittedSST +
                  I(RefittedSST^2) +
                  RefittedAreaRain +
                  I(RefittedAreaRain^2) +
                  # CoupleExpLocal +
                  (1|WORKYEAR),# + (1|ANILLOHEMB),
                na.action = "na.fail", REML = FALSE,
                data = LmmData)


sjPlot::tab_model(Lmm_full)

# Plot
plot(allEffects(Lmm_full))
```
```{r}
# Final results
Summary <- summary(Lmm_full)
FixCoef <- Summary$coefficients %>% as.data.frame() %>% rownames_to_column("Terms")
RandCoef <- Summary$varcor %>% as.data.frame() %>% select(-var2) %>% rename(Terms = grp)
CI <- confint(Lmm_full) %>% as.data.frame() %>% rownames_to_column("Terms")
CoefTable <- CI %>% left_join(FixCoef, by = "Terms") %>% bind_rows(RandCoef)
write_csv(CoefTable, "FinalResults.csv")
```

```{r}
Predictors = c("Ulna", "Laying date", "Cohabitation time", "Chl", "Chl²","SST", "SST²","Rain", "Rain²")
read.csv("FinalResults.csv") %>% select(-var1) %>% 
  mutate(across(where(is.numeric), ~round(., digits = 2))) %>%
  unite("IC", `X2.5..`:`X97.5..`, sep = " | ") %>% select(-vcov, -sdcor) %>%
  dplyr::slice(c(-(1:3), -(13:14))) %>%
  relocate(IC, .after = t.value) %>% 
  mutate(Terms = Predictors) %>% 
  kbl(col.names = c("Terms", "β", "SE", "Z", "IC"), align = c("l", "c", "c", "c", "c")) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>% 
  add_header_above(c("Chick A body mass (n = 5355)" = 5)) %>% 
  save_kable("FixMass_results.png", zoom = 10)

read.csv("FinalResults.csv", row.names = 1) %>% select(-var1) %>% round(digits = 2) %>%
  rownames_to_column("Random effects") %>% select(`Random effects`, sdcor, vcov) %>%
  dplyr::slice(c(13)) %>%
  kbl(col.names = c("Random effects", "σ", "σ²"), align = c("l", "c", "c")) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>% 
  save_kable(file = "RandMass_results.png", zoom = 10)
```


## Select random effect
```{r}
# Lmm_null = lm(BodyCondSMI ~
#                   PROPORTIONALRANK +
#                   RefittedChl +
#                   I(RefittedChl^2) +
#                   RefittedWind +
#                   I(RefittedWind^2) +
#                   RefittedSST +
#                   I(RefittedSST^2) +
#                   AGEHEMB +
#                   I(AGEHEMB^2) +
#                   LastParentalCare_ALL +
#                   # AGEMACH +
#                   # I(AGEMACH^2) +
#                   CoupleExpLocal,
#                 data = LmmData)
# Lmm_A = update(Lmm_full, . ~ . - (1|WORKYEAR))
# Lmm_W = update(Lmm_full, . ~ . - (1|ANILLOHEMB))
# ```
# ```{r}
# anova(Lmm_W, Lmm_full, refit = FALSE)
# ```
# ```{r}
# anova(Lmm_A, Lmm_full, refit = FALSE)
# ```
# ```{r}
# anova(Lmm_A, Lmm_W, refit = FALSE)
```
ANILLOHEMB as random effect is not needed


## Model Selection
```{r, eval=FALSE}
drg = dredge(Lmm_full)
head(drg, n = 10)
delta2=get.models(drg,subset= delta < 2)
summary(model.avg(delta2))
```
```{r, eval=FALSE}
one=get.models(drg,subset= 1);sjPlot::tab_model(one)
```
